Cryptographic assurance of secrecy and fairness in voting

### 2012-12-08 paper/paper.tex
pret-a

While both systems provide the voter some assurance that the proper vote was recorded, \term{Scantegrity}'s
verification process is more direct and provides a stronger guarantee that the ballot \emph{actually
cast} was recorded properly.

>>>>

While each system provides the voter some assurance that the proper vote was recorded, \term{Scantegrity}'s
verification process is more direct and provides a stronger guarantee that the ballot \emph{actually
cast} was recorded properly.
